% One-page resume tailored for the Georgia Tech OMSCS application.
% This is intentionally separate from Apoorv_Darshan_Resume.tex.

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage[english]{babel}

\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\pagestyle{empty}
\raggedright
\setlength{\tabcolsep}{0pt}
\setlength{\parindent}{0pt}
\addtolength{\oddsidemargin}{-0.62in}
\addtolength{\evensidemargin}{-0.62in}
\addtolength{\textwidth}{1.24in}
\addtolength{\topmargin}{-0.66in}
\addtolength{\textheight}{1.30in}

\titleformat{\section}
  {\vspace{-2pt}\scshape\raggedright\large}
  {}{0em}{}[\titlerule\vspace{-5pt}]

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in,nosep,itemsep=1pt,topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}
\newcommand{\resumeItem}[1]{\item\small #1}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProject}[2]{
  \item\small
  \textbf{#1} --- #2\vspace{-1pt}
}

\begin{document}

\begin{center}
  {\Huge\textbf{Apoorv Darshan}}\\[4pt]
  \small
  +91 9770514461 \ $|$ \
  \href{mailto:ad13dtu@gmail.com}{\underline{ad13dtu@gmail.com}} \ $|$ \
  \href{https://github.com/apoorvdarshan}{\underline{github.com/apoorvdarshan}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of the People}{Jun 2025 -- Jun 2026}
    {Bachelor of Science in Computer Science; GPA: 3.77/4.00, Magna Cum Laude}{Pasadena, CA, USA}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Full Stack Developer Intern}{Nov 2025 -- Feb 2026}
    {XIRCLS}{Remote}
  \resumeItemListStart
    \resumeItem{Built end-to-end CRM features for leads, accounts, authentication, reminders, and interactions using React, React Query, REST APIs, and database-backed services.}
    \resumeItem{Resolved schema, UUID, authorization, and session-cache issues; strengthened ownership validation and data integrity across frontend and backend flows.}
    \resumeItem{Led task coordination and code review for five interns while improving pagination, filtering, soft-delete/restore, validation, and real-time interface updates.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Projects and Open Source}
\resumeSubHeadingListStart
  \resumeProject{\href{https://github.com/apoorvdarshan/fud-ai}{fud-ai} $|$ 269 GitHub stars, 4K+ downloads}{AI-powered calorie and nutrition tracker released for mobile platforms.}
  \resumeProject{\href{https://github.com/apoorvdarshan/scowld}{scowld}}{Open-source SwiftUI AI companion with a live VRM avatar and camera-based visual awareness.}
  \resumeProject{\href{https://github.com/apoorvdarshan/verceltics}{verceltics}}{Native iOS application for monitoring Vercel web analytics.}
  \resumeProject{\href{https://github.com/apoorvdarshan/crossposter}{crossposter}}{Multi-platform publishing tool for X, LinkedIn, Bluesky, Mastodon, Instagram, YouTube, and other services.}
  \resumeProject{\href{https://github.com/apoorvdarshan/TetherShot}{TetherShot}}{macOS menu-bar utility that captures screenshots from a USB-connected iPhone into a selected folder.}
  \resumeProject{\href{https://github.com/pulls?q=is\%3Apr+author\%3Aapoorvdarshan+is\%3Amerged}{Open-source contributions}}{Merged fixes across TensorFlow, Flutter, Kubernetes, Svelte, jQuery, Spring Boot, freeCodeCamp, and other widely used projects.}
\resumeSubHeadingListEnd

\section{Honors}
\resumeItemListStart
  \resumeItem{Magna Cum Laude, B.S. Computer Science, University of the People.}
  \resumeItem{President's List and Dean's List, University of the People.}
  \resumeItem{CodeChef Problem Solver Diamond Badge for completing 1,000 programming problems.}
  \resumeItem{JEE 2023: ranked in the top 1.5\% nationally.}
  \resumeItem{Indian Mathematics Olympiad (IOQM/RMO): placed among the top 300 in Madhya Pradesh and advanced to the regional round.}
\resumeItemListEnd

\section{Technical Skills}
\small
\textbf{Languages:} JavaScript, TypeScript, Python, Swift, Kotlin, Dart, Java, C, SQL, HTML/CSS \\
\textbf{Frameworks:} React, Next.js, Node.js, Express, Flutter, SwiftUI, Jetpack Compose, React Query, Tailwind CSS \\
\textbf{Tools and Platforms:} PostgreSQL, MongoDB, Supabase, Git, GitHub, Docker, Vercel, REST, GraphQL, iOS, Android, macOS, Linux

\end{document}
